---
title: "Assessment 1.1"
author: "Chiu Yee Lim 4663994"
date: "01/09/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(knitr)
library(skimr)
library(ggplot2)
```

### Part 1

# RMarkdown

***R Markdown provides an authoring framework for data science. You can use a single R Markdown file to save and execute code or generate high quality reports that can be shared with an audience. R markdown documents are fully reproducible and support dozens of static and dynamic output formats.***

[link](https://rmarkdown.rstudio.com/lesson-8.html)

### Q6

```{r}
fastfood <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-09-04/fastfood_calories.csv")
```

### Q7

```{r}
fastfood %>% head(10)
```

```{r}
knitr::kable(fastfood[1:10, 1:5])
```

### Q8: More than 1000 calories

```{r}
fastfood %>%
  filter(calories > 1000)
```

### Q9: New Variable(dont_eat_this)

```{r}
dont_eat_this<-fastfood %>%
  filter(total_fat>40 & total_carb>80)
```

### Q10: Mcdonalds

```{r}
fastfood %>%
  filter(restaurant == 'Mcdonalds')
```


### Part 2

### Q11: 'skimr' package

```{r}
fastfood %>% skim()
```

### Q12: Count of each restaurant

```{r}
fastfood %>%
  count(restaurant)
```

### Q13: Grouppings

```{r}
fastfood %>%
  group_by(restaurant) %>%
  summarize(average_cal = mean(calories))
```

### Q14: New variable(average_calories)

```{r}
average_calories<-fastfood %>%
  group_by(restaurant) %>%
  mutate(average_calories = mean(calories)) %>%
  ungroup()
```

### Q15: Data Vis of total fat

```{r}
fastfood %>%
  ggplot(aes(restaurant,total_fat, fill=restaurant))+
  geom_col()
```

#### On column chart, it represent the categories (restaurant) by using X axis (horizontal axis) and represent the numerical or data (total_fat) by using Y axis (vertical axis). By using column charts, we can easily to read and understand the difference between all the categories depends on the height differences.


### Q16: New variable(max_total_fat)

```{r}
max_total_fat<-fastfood %>%
  group_by(restaurant) %>%
  mutate(max_total_fat = max(total_fat)) %>%
  ungroup()
```

### Q17: geom_point

```{r}
fastfood %>%
  filter(restaurant == 'Mcdonalds') %>%
  ggplot(.,aes(sugar,protein))+
  geom_point()
```


### Part 3

### Q18: Factors

```{r}
fastfood$restaurant<-as_factor(fastfood$restaurant)
class(fastfood$restaurant)
```

### Q19 Cut_number

```{r}
fastfood<-fastfood %>%
  mutate(calories_type = cut_number(fastfood$calories, 3, labels = c("low", "med","high")))
```

### Q20: Data Viz (calories_type)

```{r}
fastfood %>% 
  count(restaurant, calories_type, sort=TRUE) %>% 
  ggplot(aes(n,calories_type,fill=factor(calories_type))) +
  geom_col() +
  coord_flip() +
  facet_wrap(~restaurant) +
  theme_linedraw()
```

### Q21: New variable (trans_fat_percent)

```{r}
fastfood<-fastfood%>%
  mutate(trans_fat_percent = round (fastfood$trans_fat/fastfood$total_fat*100,2))
```

### Q22: Data Vis (trans_fat)

```{r}
fastfood%>%
  ggplot(aes(restaurant, trans_fat, color=restaurant, fill=restaurant)) + 
  geom_point(alpha=0.4, position="jitter")
```

### Q23: average of total fat

```{r}
fastfood %>%
  group_by(restaurant) %>%
  summarise(average_fat = mean(total_fat))
```

### Q24: Data viz (total fat)

```{r}
fastfood%>%
  ggplot(aes(restaurant, total_fat,fill=restaurant)) +
  geom_boxplot()
```

